---
title: "Untitled"
description: |
  A new article created using the Distill format.
author:
  - name: Nora Jones 
    url: https://example.com/norajones
    affiliation: Spacely Sprockets
    affiliation_url: https://example.com/spacelysprokets
date: "`r Sys.Date()`"
output: distill::distill_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
## Footnotes
Sometimes all the information is not in the body ^[Because it is in the footer]. 
When you do that you'll add footnotes ^[By adding footnote syntax].

## Asides
### Asides can be text.
<aside>
This comment is on the side.
</aside>

### They can also be output from code chunks such as plots.
<aside>
```{r} 
plot(cars) 
```
</aside>

## Appendices
Appendices are added at the end of the document by adding {.appendix} after any level 1 (#) or level 2 (##) header.

This makes sense for, e.g., acknowledgments or author's notes.

## Acknowledgments {.appendix}
You can recognize people and institutions in acknowledgments.
